surfing

### 2021-06-29 inst/surfing.Rmd
work

```{r}  
plot(p,l,type='b',xlab="compatriot support",ylab="support")
```

```{r}
scomp3
maxp(scomp3)
specificp.gt.test(scomp3,'S',0)
````

>>>>

```{r}  
plot(p,l,type='b',xlab="compatriot support",ylab="support",main="profile support for S, scomp")
```

```{r cache=TRUE}
scomp3
maxp(scomp3)
specificp.gt.test(scomp3,'S',0,n=100)
````

```{r profsuppcalcscomp3atriotmonster, cache=TRUE}
p <- c(0.0002,seq(from=0.001,to=0.02,len=10))
l <- profsupp(scomp3,"S",p,relative=FALSE,n=100)
```

```{r}  
plot(p,l,type='b',xlab="compatriot support",ylab="support",main="profile support for S, scomp3")
```
